Income Disparity and Its Influence on Higher Education Affordability and Access

### 2024-02-13 starter_folder-main 4/paper/paper.qmd
updated paper

# Set the file path (Updated to the new path)
file_path <- "../data/analysis_data/college_tuition_fees_analysis_data.csv"

# Read the data from the CSV file (Updated function and removed sheet/range arguments)
data <- read_csv(file_path)

>>>>

# Set the file path 
file_path <- "../data/analysis_data/college_tuition_fees_analysis_data.csv"

# Read the data from the CSV file
data <- read_csv(file_path)
